Spatial Analysis

### 2021-12-08 Scripts/spatial_analisis.Rmd
misc

# Create specific state pallet from our friend Wes Andersson
state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 5, name = "Darjeeling2"),
                               wes_palette(n = 3, name = "Royal1")
                  )

@@

# State pallet

@@

@@

@@

# Load grid of fishing ports
grid_eez_fp_sf <-  st_read(my_path("D","Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
  select(index,abrev,geometry) %>% 
  mutate(method = "fishing_port"#,
         # state = str_to_sentence(landing_port)
         )%>% 
  left_join(state_lat)

>>>>

# Create specific state pallet from our friend Wes Andersson

@@

@@

### NUmbers for papaer

@@

### Figure plotting

@@

# Load grid of fishing ports
grid_eez_fp_sf <-  st_read(my_path("D","Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
  select(index,abrev,geometry) %>% 
  mutate(method = "fishing_port"#,
         # state = str_to_sentence(landing_port)
         ) %>% 
  left_join(state_lat)
